### 2010-06-25 resume_cv/cv.tex
Updated my cv and list of applications just a bit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Awards}
%
Brigham Young University
\begin{innerlist}
\item National Merit Scholarship, 2004--2010
\item Inducted into the Phi Kappa Phi Honors Society, 2009
\item Barry M. Goldwater Scholarship Nominee, 2009
\item Claricode Medical Essay Scholarship Finalist, 2009
\end{innerlist}

@@

\section{Conference Publications} \begin{bibsection}
    \item Andrew McNabb, Matthew Gardner, and Kevin Seppi. An Exploration of
	  Topologies and Communication in Large Particle Swarms.  In:
	  \emph{Congress on Evolutionary Computation, 2009}.

	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  Submitted to:
	  \emph{Transactions on Evolutionary Computation}.  Awaiting acceptance
	  notification.
\end{bibsection}

@@

\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.  Official blog post about
  my project can be found at:
  http://google-tmads.blogspot.com/2010/01/track-cost-per-call-data-through-google.html.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}

@@

>>>>

@@

\section{Awards}
%
Brigham Young University
\begin{innerlist}
\item National Merit Scholarship, 2004--2010
\item Awarded a research grant from the Office of Research and Creative
  Activities in both 2008 and 2009
\item Inducted into the Phi Kappa Phi Honors Society, 2009
\item Barry M. Goldwater Scholarship Nominee, 2009
\item Claricode Medical Essay Scholarship Finalist, 2009
\end{innerlist}

@@

@@

\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.  Official blog post about
  the project can be found at:
  http://google-tmads.blogspot.com/2010/01/track-cost-per-call-data-through-google.html.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}

@@

\section{Publications} \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  In: \emph{Parallel Problem
	  Solving in Nature, 2010}.

    \item Andrew McNabb, Matthew Gardner, and Kevin Seppi. An Exploration of
	  Topologies and Communication in Large Particle Swarms.  In:
	  \emph{Congress on Evolutionary Computation, 2009}.
\end{bibsection}
